---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# OfflineGeocodeR

`OfflineGeocodeR` provides a wrapper around calling a Docker container (`DeGAUSS/geocoder_slim`) in order to geocode addresses from R without using the internet. This is advantageous for several reasons, two of which are maintaining the privacy of protected health information and maintaining a reproducible research workflow.  See our manuscript about using DeGAUSS (Decentralized Geomarker Assessment for Multi-Site Studies) [here]().

## Installing

OfflineGeocodeR is a private package hosted on GitHub.

Install with:

```{r eval=FALSE}
remotes::install_github('cole-brokamp/OfflineGeocodeR')
```

You must also have Docker installed and available on your system. In the future, it will hopefully be possible to use this package to call a remote docker machine, but for now, it must be local.

*Note: This package was originally designed as a personal convenience and has not been tested on setups other than unix-based operating systems with Docker running natively (i.e. not Docker Toolbox). Your mileage may vary*
